\LARGE \bf A Hybrid Control Framework for Autonomous Vehicles at Uncontrolled Intersections

### 2019-01-17 conference/iv2019/manuscript.tex
done with experimental section

\subsubsection{Smoothness}

@@

>>>>

Table \ref{tb:speeds} shows a summary of the average speed compared to the baseline speed of 4.4 m/s.

\begin{table}[h]
\footnotesize
\begin{center}
\caption{Average Vehicle Speed}\label{tb:speeds}
\begin{tabular}{cccc}
Pedestrian Entry & Vehicle Lane & Average Speed (m/s) & Pct. of Baseline \\\hline\hline

Right Side & Right-Most & 2.90 & 66\% \\
Right Side & Second-to-Right & 2.93 & 67\% \\
Left Side  & Right-Most & 4.4 & 100\% \\
Left Side  & Second-to-Right & 2.80 & 64\% \\\hline

\end{tabular}
\end{center}
\end{table}

\subsubsection{Smoothness}
The requirement of keeping a low acceleration where possible is validated through the middle rows of Fig.\ref{fig:velPlot1} and Fig.\ref{fig:velPlot2}.The vehicle is able to maintain a peak acceleration of 2 $\mathrm{m/s^2}$ for the vast majority of simulated trials, particularly when the pedestrian crosses from the opposing side of the road or when the vehicle is in the second to right line.

However, there are a handful of simulated trials in Fig.\ref{fig:velPlot1} when the pedestrian accepts a gap between 1.75-2.5 seconds and the vehicle is in the right-most lane closest to the sidewalk. In this case, the vehicle must enter the \textit{Hard Braking} state and decelerate at a magnitude higher than $a_\mathrm{cmf}$. This is required in order to meet the collision avoidance constraint, which naturally takes priority. Again, note that this situation occurs relatively rarely, as pedestrians typically accept gaps between 3-6 seconds and are unlikely to risk hazardous behaviors unless distracted.

\begin{figure}[h]
\centering
\includegraphics[width=3.0in]{figures/G80.jpg}
\caption{Hyundai Genesis G80 experimental testbed.}
\label{fig:g80}
\end{figure}

@@

The proposed hybrid controller is tested experimentally using a Hyundai Genesis G80 experimental testbed, shown in Fig. \ref{fig:g80}. A mid-block intersection at Richmond Field Station near Berkeley's campus was chosen for the experimental validation.  In lieu of an actual pedestrian, a pedestrian was simulated virtually using the ROS simulation architecture described earlier, with the position of the pedestrian sent to the vehicle in real time. Differential GPS was used to record the distance to the crosswalk, and a steering controller from \cite{kapania} was used to autonomously steer the vehicle in a straight line path. Relevant parameters of the experiments are shown below in Tables \ref{tb:expparams}.

\begin{table}[h]
\footnotesize
\begin{center}
\caption{Experimental Parameters}\label{tb:expparams}
\begin{tabular}{lccc}
Parameter & Symbol & Value & Units \\\hline\hline
Number of lanes & $n$ & 2 & - \\
Speed feedback gain & $k_s$ & 2.0 & 1 / sec\\
Brake time delay    & $t_\mathrm{delay}$ & 0.5 & sec \\ 
Speed limit & $v_\mathrm{speedlimit}$ & 7 & m/s \\
Comfort acceleration & $a_\mathrm{cmf}$ & 2 & $\mathrm{m/s^2}$ \\
Maximum time advantage & $t_\mathrm{max}$ & 4 & sec \\
Maximum acceleration & $a_\mathrm{max}$ & 9 & $\mathrm{m/s^2}$ \\\hline
\end{tabular}
\end{center}
\end{table}

Several key differences to highlight between the simulations and the experiments are that the number of lanes is decreased from 4 to 2 and that the speed limit is increased to 7 m/s to match the parameters of the experimental intersection. The experiment consisted of six trials intended to show operation of the four discrete modes of the controller. A description of the trial parameters are shown in Table \ref{tb:expparams2}.

\begin{table}[h]
\footnotesize
\begin{center}
\caption{Experimental Parameters}\label{tb:expparams2}
\begin{tabular}{llll}
Trial Number & Gap Accepted (sec) & Pedestrian Entry & Mode\\\hline\hline
1 & 4.0 & right &  Yield\\ 
2 & 1.0 & right &  Speed Up\\ 
3 & 7.0 & right &  Yield\\ 
4 & 2.5 & right &  Hard Brake\\ 
5 & 3.0 & left  &  Yield \\ 
6 & 1.0 & left  &  Speed Up\\\hline
\end{tabular}
\end{center}
\end{table}

The experimental velocity and acceleration is plotted vs $d$ in 
Figure \ref{fig:diagram1}. In Trial 1, the virtual pedestrian enters when the vehicle is four seconds from intersecting, giving the vehicle enough time to yield at a deceleration of 2 $m/s^2$. Note that the vehicle exhibits a large time delay between commanded and actual acceleration. Because this is accounted for in Algorithm 1, the vehicle is able to brake early and the vehicle is nearly stopped at $d = $ 1 meter before the pedestrian exits the crosswalk and the vehicle speeds back up. This overshoot, while undesirable, is realistically acceptable given the point $d=0$ is set to be several meters before the crosswalk actually begins.

\begin{figure}[h]
\centering
\includegraphics[width=3.5in]{figures/expPlot.eps}
\caption{Experimental velocity and acceleration plotted vs distance to crosswalk. Note that the sign of $d$ is opposite that of Fig.\ref{fig:diagram1}}
\label{fig:g80}
\end{figure}

In Trial 2, the pedestrian enters from the right with just 1 second before collision. This experiment, while unlikely in reality, was undertaken to verify the vehicle would not brake, but accelerate through the intersection. Trial 3 represents a situation where the pedestrian crosses with a large (7 second) gap. In this case, the pedestrian has enough time to almost cross before the vehicle needs to yield, resulting in the vehicle only needing to slow down slightly.

In Trial 4, the pedestrian exhibits risky behavior, crossing with a 2.5 second gap. In this case, the vehicle has enough time to brake, but must decelerate rapidly at 5 $m/s^2$ in the \textit{hard braking} mode. Given the brake delay in the experimental vehicle, significant overshoot occurs, and the vehicle stops nearly 2.5 meters ahead of the desired stopping location. Unlike in the yielding mode, the brake delay can not be compensated for because the vehicle must brake suddenly.

Trials 5 and 6 represent pedestrian crossings from the opposite side of the road under accepted gaps of 3.0 and 1.0 seconds, respectively. In the former case, the vehicle is able to yield in a fashion similarly to Trial 1, and in the latter case, the vehicle is able to speed through the intersection, as in Trial 2.
